SIR Model With Testing Flows and Isolation

### 2020-11-30 codes/ali_test_sir.Rmd
updated the tex, code, pix

which(df2[]<0)
```

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
    theme(panel.spacing=grid::unit(0,"lines"))
p1_temp <- (p1
    + geom_contour_filled(breaks=pretty(unique(df2$R0_sub),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
)
p1_temp
# ggsave(p1_temp,filename = "R0contour_random.png" , path="../pix/")
ggsave(p1_temp,filename = "R0contour_TTI.png" , path="../pix/")

>>>>

df2_fake <- df2 %>% dplyr::select(eta_t,eta_w)
df2_fake <- unique(df2_fake) %>% dplyr::mutate(flag=ifelse(eta_t<=eta_w,1,0))
```

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
    theme(panel.spacing=grid::unit(0,"lines"))
p1_temp <- (p1
    + geom_contour_filled(breaks=pretty(unique(df2$R0_sub),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
    + geom_rect(data=df2,
                          fill=ifelse(df2$eta_t>df2$eta_w,"white","NA" ),
                          color= NA,
                          ymin=-1,
                          ymax=10,
                          xmin=-1,
                          xmax=2)
    )
p1_temp

# ## hack (By Dr. Ben Bolker) white rectangle to cover grid
#   ggplot() + 
#   scale_x_continuous(name="x") + 
#   scale_y_continuous(name="y") +
#   facet_grid(eta_w~eta_t, labeller=label_special) +
#     geom_rect(data=df2_fake,
#                           fill=ifelse(df2_fake$eta_t>df2_fake$eta_w,"white","black"),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)

# ggsave(p1_temp,filename = "R0contour_random.png" , path="../pix/")
# ggsave(p1_temp,filename = "R0contour_TTI.png" , path="../pix/")
